Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-22 manuscript_covid19dashboard.Rmd
Updated introduction

Given such available data, it is important to develop tools for exploratory analysis for

>>>>

In the response to the COVID-19 pandemic, massive amounts of data are being generated. Given such available data, it is critical to create tools for exploratory analysis for policymakers, health officials, and the general public.
